Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-22 manuscript/manuscript.Rmd
added policy plot

One problem that is often encountered when using machine learning methods is the interpretability of the output of these methods.
In our case, the output is a policy function parametrized by a neural network $\theta$:
\begin{align*}
  \pi_\theta: N_t \mapsto (M_X(N_t), M_Y(N_t)),
\end{align*}
where $N_t=(X_t,Y_t,Z_t)$ is the state of the system at time $t$, and where $M_X$ and $M_Y$ are the mortalities due to harvest during that time-step.
Here we visualize this policy function and provide an interpretation for it.
Given its high dimension, it is not possible to fully display how the policy function obtained ‘‘looks like’’---we thus project it down to certain relevant axes.
The result of this procedure is shown in Fig. **TBD**.
In that figure, the shape of the optimal escapement strategy is provided for comparison.

>>>>

One problem that is often encountered when using machine learning methods is the interpretability of the output of these methods.
In our case, the output is a policy function parametrized by a neural network $\theta$:
\begin{align*}
  \pi_\theta: N_t \mapsto (M_X(N_t), M_Y(N_t)),
\end{align*}
where $N_t=(X_t,Y_t,Z_t)$ is the state of the system at time $t$, and where $M_X$ and $M_Y$ are the mortalities due to harvest during that time-step.
Moreover, in the case of our ‘‘PPO+GP’’ management strategy, we sample $\pi_\theta$ on a grid of points $G={(X_i, Y_i, Z_i)}_i$ and use a Gaussian process to interpolate $\pi_\theta$, i.e.
\begin{align}
  \pi_{\text{PPO+GP}} = \text{Gaussian process interpolation of } \pi_\theta|_G.
\end{align}
This process was explained in detail in the Methods section.

Here we visualize the resulting $\pi_{\text{PPO+GP}}$ policy and provide an interpretation for it.\footnote{
A similar characterization of $\pi_\theta$ is found on the appendix. 
Here we focus on the Gaussian process interpolation as it is smoother and, thus, easier to interpret.
}
Given its high dimension, it is not possible to fully display how the policy function obtained ‘‘looks like’’---we thus project it down to certain relevant axes.
The result of this procedure is shown in Fig. \ref{fig:gpp-policy}.
In that figure, the shape of the optimal escapement strategy is provided for comparison.

\begin{figure}
  \centering
  \includegraphics[scale=0.25]{figures/gpp-policy-pdf.pdf}
  \caption{Plots of the PPO+GP policy $\pi_{\text{PPO+GP}}$ along several relevant axes. Here $M_X$ and $M_Y$ are the $X$ and $Y$ components of the policy function. The values of the plots are generated in the following way: For each variable $X$, $Y$, and $Z$, the times-eries of evaluation episodes are used to generate a window of typical values that variable attains when controlled by $\pi_{\text{PPO+GP}}$. Then, for each plot either $X$ or $Y$ was varied on $[0,1]$ along the $x$ axis, while the other variables (resp. $Y$ and $Z$, or $X$ and $Z$) were varied within the typical window computed before. The value of one of the latter two variables were visualized as color.}
  \label{fig:gpp-policy}
\end{figure}
